HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-09-21 scnn.tex
bugfix when referencing to appendix

The simulations are created using the fast lightcone method \pkg{UFalcon} described in \citep{sgier2018fastgeneration}. A brief overview about the map making procedure used in \pkg{UFalcon} is given in \recref{convergence_mass_maps} and the specific simulation setup is given in \recref{simulation_setup}.
We however use a single simulation box, as opposed to two used in that work, as we use source galaxies at a lower redshift of $z=0.8$, instead of $z=1.5$.
As a simulator we use \pkg{L-PICOLA} \citep{howlett2015lpicola}, a fast and approximate code for N-body simulations.
For each class, we generate $30$ simulations.
Out of the $60$ simulations, $20$ are kept as the test set, and $20\%$ of the remaining training data is used as a validation set, to monitor the training process and select the hyper-parameters.
\figref{map_sample} shows the whole sky simulations and a zoom region for both models.
Initial conditions for these simulations are the same, so the differences in structures can only be attributed to different cosmological parameters used to evolve the particle distribution.

>>>>

The simulations are created using the fast lightcone method \pkg{UFalcon} described in \citep{sgier2018fastgeneration}. A brief overview about the map making procedure used in \pkg{UFalcon} is given in \ref{sec:convergence_mass_maps} and the specific simulation setup is given in \ref{sec:simulation_setup}.
We however use a single simulation box, as opposed to two used in that work, as we use source galaxies at a lower redshift of $z=0.8$, instead of $z=1.5$.
As a simulator we use \pkg{L-PICOLA} \citep{howlett2015lpicola}, a fast and approximate code for N-body simulations.
For each class, we generate $30$ simulations.
Out of the $60$ simulations, $20$ are kept as the test set, and $20\%$ of the remaining training data is used as a validation set, to monitor the training process and select the hyper-parameters.
\figref{map_sample} shows the whole sky simulations and a zoom region for both models.
Initial conditions for these simulations are the same, so the differences in structures can only be attributed to different cosmological parameters used to evolve the particle distribution.
